\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\usepackage{longtable}

\title{CopyForward Publishing (CFP)\\Final Report}
\author{Project Team}
\date{\today}

\begin{document}
\maketitle

\section{Introduction}

This report describes the design and implementation of the CopyForward Publishing (CFP) web application.
The system is built on a LAMP stack (Linux/Apache/MariaDB/PHP) and supports open-access items, donations,
committee workflows, and an anti-plagiarism process.

\section{Requirements Overview}

\begin{itemize}
  \item Roles: admin, moderator, author, member.
  \item Workflows: upload/approval, downloads with limits, donations with splits, committee discussions and voting, blacklisting and suspension.
  \item Reporting: statistics by item and author, donation summaries, CSV exports.
\end{itemize}

\section{Database Design and Normalization}

See \texttt{db/schema.sql} and \texttt{docs/design\_notes.md} for the full relational schema and 3NF justification.
Key entities include members, authors, items, item\_versions, downloads, donations, committees, discussions, votes,
comments, internal\_messages, moderation\_logs, and daily statistics tables.

\section{Application Architecture}

The application is organized as:

\begin{itemize}
  \item \texttt{src/public}: web entry points (index, login/register, role-specific pages).
  \item \texttt{src/includes}: shared helpers (database, auth, session/role checks).
  \item \texttt{src/admin}, \texttt{src/author}, \texttt{src/member}, \texttt{src/moderator}: role-specific workflows.
  \item \texttt{assets}: CSS and JavaScript.
  \item \texttt{scripts}: utility scripts (statistics aggregation, packaging).
\end{itemize}

\section{Key Workflows}

\subsection{Authentication and Roles}

Describe login, registration, session handling, and role-based access checks.

\subsection{Uploads and Approvals}

Describe how authors upload items and how moderators approve or reject them.

\subsection{Downloads and Donation Rules}

Summarize the business rules for download limits (1 per 7 days or 1/day for recent donors) and donation splits
(at least 60\% to charity).

\subsection{Plagiarism, Blacklisting, and Suspension}

Summarize the plagiarism reporting, committee voting with 2/3 majority logic, item blacklisting, and automatic
author suspension after three blacklisted items.

\section{User Interface}

Provide screenshots and descriptions of the main pages for each role (home/search, item detail, author dashboard,
member profile, moderator dashboard, admin statistics).

\section{Installation and Deployment}

Summarize the key steps from \texttt{INSTALL.md}, including database setup, configuration of \texttt{db.php},
and running the PHP server or Apache virtual host.

\section{Testing}

Reference the test notes in \texttt{docs/tests\_phase3.md} and \texttt{docs/tests\_phase5.md}, and describe any
additional manual or automated tests performed.

\section{Team Contributions}

Describe individual responsibilities and contributions for each team member.

\section{Conclusion}

Summarize the project outcomes, limitations, and possible future enhancements (e.g., stronger auth matrix logic,
file storage, more detailed reporting).

\end{document}


